23-Figure2-051321

### 2022-05-12 notebooks/23-FigureS6-S7.Rmd
figure S6-S7

# Load input dataframe
```{r}
# smake<-setClass("smake",slots=list(input="list"))
# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv", "pcc_df"='../data/interim/pcc_df.csv',"sensors_pcc"="../data/interim/sensors_df.csv",'effector_pcc'='../data/interim/effectors_df.csv',
# "rwr_row"="../data/interim/rwr_ranked_goa_rows.csv","prs_row"="../data/interim/prs_ranked_goa_rows.csv",
# "rwr_column"="../data/interim/rwr_ranked_goa_columns.csv","prs_column"="../data/interim/prs_ranked_goa_columns.csv"))
```

@@

@@

```{r}
if(snakemake@params['save']==TRUE){
  figure_folder = "reports/figures/paper_figures_052521/"
combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))
ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=12,height=12)
}
```

>>>>

# Load input dataframe
```{r}
# smake<-setClass("smake",slots=list(input="list"))
# nw_type = 'coessentiality'
# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv",
#                                     "pcc_df"=glue('../data/interim/{nw_type}/{nw_type}_df_human.csv'),
#                                     "pcc_df_random"=glue('../data/interim/{nw_type}/{nw_type}_df_random_500_human.csv')))

```{r}
# smake<-setClass("smake",slots=list(input="list"))
# nw_type = 'pombe'
# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv",
#                                     "pcc_df"=glue('../data/interim/{nw_type}/{nw_type}_df_corr.csv'),
#                                     "pcc_df_random"=glue('../data/interim/{nw_type}/{nw_type}_df_random_500_corr.csv')))

@@

```{r}
combined_rewire_df %>% filter(type != "real")%>%summary()
```

@@

```{r}
#if(snakemake@params['save']==TRUE){
  figure_folder = glue("../reports/figures/paper_figures_{nw_type}/")
combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))
ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=12,height=12)
#}
```

```{r}
